### 2025-04-16 multiple-regression.qmd
20250416 - update formulas

where $p$ is the number of [predictor variables](#sec-correlationalStudy).

@@

@@

```{r}
quadraticTermsRegressionModel <- lm(
  fantasyPoints ~ age + I(age^2) + height + I(height^2) + weight + I(weight^2) + target_share + I(target_share^2),
  data = player_stats_seasonal %>% filter(position %in% c("WR")),
  na.action = "na.exclude"
)

summary(quadraticTermsRegressionModel)
```

@@

>>>>

where $p$ is the number of [predictor variables](#sec-correlationalStudy).
Multiple regression is basically a weighted sum of the [predictor variables](#sec-correlationalStudy), and adding an intercept.
Under the hood, multiple regression seeks to identify the best weight for each [predictor](#sec-correlationalStudy).

@@

linearRegressionModel_beta0 <- coef(quadraticTermsRegressionModel)[["(Intercept)"]]
linearRegressionModel_beta1 <- coef(quadraticTermsRegressionModel)[["age"]]
linearRegressionModel_beta2 <- coef(quadraticTermsRegressionModel)[["height"]]
linearRegressionModel_beta3 <- coef(quadraticTermsRegressionModel)[["weight"]]
linearRegressionModel_beta4 <- coef(quadraticTermsRegressionModel)[["target_share"]]
```

The model formula with substituted values is in @eq-linearRegressionModelSubstitute:

$$
\begin{aligned}
  \text{fantasy points} = &\beta_0 + \beta_1 \cdot \text{age} + \beta_2 \cdot \text{height} + \beta_3 \cdot \text{weight} + \beta_4 \cdot \text{target share} + \epsilon \\
  = &`r petersenlab::apa(linearRegressionModel_beta0, decimals = 2)` + `r petersenlab::apa(linearRegressionModel_beta1, decimals = 2)` \cdot \text{age} + `r petersenlab::apa(linearRegressionModel_beta2, decimals = 2)` \cdot \text{height} + `r petersenlab::apa(linearRegressionModel_beta3, decimals = 2)` \cdot \text{weight} + `r petersenlab::apa(linearRegressionModel_beta4, decimals = 2)` \cdot \text{target share} + \epsilon
\end{aligned}
$$ {#eq-linearRegressionModelSubstitute}

@@

```{r}
quadraticTermsRegressionModel <- lm(
  fantasyPoints ~ age + I(age^2) + height + I(height^2) + weight + I(weight^2) + target_share + I(target_share^2),
  data = player_stats_seasonal %>% filter(position %in% c("WR")),
  na.action = "na.exclude"
)
```

The model formula is in @eq-quadraticTermsRegressionModel:

$$
\begin{aligned}
  \text{fantasy points} \; = \; &\beta_0 + \beta_1 \cdot \text{age} + \beta_2 \cdot \text{age}^2 + \beta_3 \cdot \text{height} + \beta_4 \cdot \text{height}^2 + \\
  &\beta_5 \cdot \text{weight} + \beta_6 \cdot \text{weight}^2 + \beta_7 \cdot \text{target share} + \beta_8 \cdot \text{target share}^2 + \epsilon
\end{aligned}
$$ {#eq-quadraticTermsRegressionModel}

```{r}
summary(quadraticTermsRegressionModel)
```

@@

We can calculate this by substituting in the regression coefficients and predictor values:

Here is the computation:

```{r}
age <- 23
height <- 72
weight <- 200
target_share <- 3

beta0 <- coef(quadraticTermsRegressionModel)[["(Intercept)"]]
beta1 <- coef(quadraticTermsRegressionModel)[["age"]]
beta2 <- coef(quadraticTermsRegressionModel)[["I(age^2)"]]
beta3 <- coef(quadraticTermsRegressionModel)[["height"]]
beta4 <- coef(quadraticTermsRegressionModel)[["I(height^2)"]]
beta5 <- coef(quadraticTermsRegressionModel)[["weight"]]
beta6 <- coef(quadraticTermsRegressionModel)[["I(weight^2)"]]
beta7 <- coef(quadraticTermsRegressionModel)[["target_share"]]
beta8 <- coef(quadraticTermsRegressionModel)[["I(target_share^2)"]]

predictedFantasyPoints <- beta0 + beta1*age + beta2*(age^2) + beta3*height + beta4*(height^2) + beta5*weight + beta6*(weight^2) + beta7*target_share + beta8*(target_share^2)
predictedFantasyPoints
```

The model formula with substituted values is in @eq-quadraticTermsRegressionModelSubstitute:

$$
\begin{aligned}
  \text{fantasy points} \; = \; &\beta_0 + \beta_1 \cdot \text{age} + \beta_2 \cdot \text{age}^2 + \beta_3 \cdot \text{height} + \beta_4 \cdot \text{height}^2 + \\
  &\beta_5 \cdot \text{weight} + \beta_6 \cdot \text{weight}^2 + \beta_7 \cdot \text{target share} + \beta_8 \cdot \text{target share}^2 + \epsilon \\
  = &`r petersenlab::apa(beta0, decimals = 2)` + `r petersenlab::apa(beta1, decimals = 2)` \cdot \text{age} + `r petersenlab::apa(beta2, decimals = 2)` \cdot \text{age}^2 + `r petersenlab::apa(beta3, decimals = 2)` \cdot \text{height} + `r petersenlab::apa(beta4, decimals = 2)` \cdot \text{height}^2 + \\
  &`r petersenlab::apa(beta5, decimals = 2)` \cdot \text{weight} + `r petersenlab::apa(beta6, decimals = 2)` \cdot \text{weight}^2 + `r petersenlab::apa(beta7, decimals = 2)` \cdot \text{target share} + `r petersenlab::apa(beta8, decimals = 2)` \cdot \text{target share}^2 + \epsilon \\
  = &`r petersenlab::apa(predictedFantasyPoints, decimals = 2)`
\end{aligned}
$$ {#eq-quadraticTermsRegressionModelSubstitute}
